\subsection{Key Ideas}
\label{key:sec}

Based on the above observations, we design {\tool} with the following
key ideas.



%Overall, these observations indicate that the names of the variables
%in a particular function not only depend on {\em the task} in which
%the variable is used to implement (called {\bf task-specific context}), but
%their names are also affected by {\em their own properties and roles} in the
%code (called {\bf single-variable usage context}) and on the {\em names of the
%other variables} in the same function (called {\bf multiple-variable usage
%  context}).


\noindent {\bf Key Idea 1.} {\em A variable name is in accordance with
  the properties of the variable} including the names of the fields
and the methods in field accesses and method calls from the variable.
The names of the fields and methods are kept intact after
minification, thus, a model can rely on those names to predict the
names of the variables. For example, a model can be trained to learn
from the variables that have the field accesses to
\code{startContainer}, \code{endContainer}, \code{startOffset}, and
\code{endOffset}, and have the method calls to \code{cloneRange()},
and used to predict the variable name \code{range}.

\noindent {\bf Key Idea 2.} {\em A variable name can be influenced by
  the names or the properties of the other variables having the
  relations with that variable}. For example, a model can be trained
from the assignment \code{preSelectionRange} =
\code{range.cloneRange()} to predict the variable name on the
left-hand side of \code{X = range.cloneRange()}. In other cases, a
model can learn the names that often appear together in several
methods in the training corpus. For example, the variable names
\code{selection}, \code{selectionState}, \code{range}, and
\code{preSelectionRange}.

\noindent {\bf Key Idea 3.} {\em We leverage the duality between the
  learning to predict the variable names and the learning to predict
  the variable types.} In the original code, the name of a variable
should be natural (unsurprising) with respect to the type of that
variable. Moreover, if one knows the name of a variable, its type
should be in accordance and follow a naming convention.  For example,
at line 24, as the model encounters \code{if (y!=-1)}, it is expected
to learn that \code{y} is of the type \code{int} and cannot be used in
the locations where a string is expected.
